a and generators

### 2022-05-03 documentos/intro.tex
Is there an award for this?

\par
In this work we present a generalization of idempotent Pauli channels, \ie{}
the qubit flip operations (bit, phase and bit-phase when the flip probability is $1/2$), total depolarizing qubit
channel and the identity channel, to the case of $N$ qubits. 
% \cpnote{Mencionar decoherencia} 
The generalization is done by extending
Pauli observables to \textit{Pauli strings} (tensor products of Pauli
matrices)~\cite{KIMURA2003339,Lawrence2002}, the resulting maps are unital and diagonal in the Pauli strings'
basis.
Moreover, these channels describe decoherence in a similar way as the aforementioned
single-qubit channels describe decoherence. \cpnote{Si alguien mejora esta
frase, de lujo}
\afnote{In addition, these channels describe the decoherence process in a similar way as the aforementioned
ones for the single-qubit case.}
We call such maps \textit{Pauli component erasing} (\pce{}) maps \afnote{From now on we refer to them as \textit{Pauli component erasing} (\pce{}) maps}. We
derive necessary and sufficient conditions for such mappings to be completely
positive trace preserving \afnote{(CPTP)}, thus, showing which idempotent operations are valid
quantum channels (\pce{} channels). Additionally, we characterize the algebraic
properties of the set of \pce{} channels, showing that \afnote{it} is equipped with a
semigroup structure, which is later used to derive physical implementations.
%
\par
The paper is organized as follows, in section~\ref{sec:pce_maps} we recall
the properties of quantum channels needed to proceed with the definition 
of 
% the tools to unders
% refreshing of quantum channels theory and the definition of 
\pce{} maps. In
section~\ref{sec:math} we diagonalize analytically the Choi matrix for
arbitrary \pce{} maps and characterize completely positive maps by interpreting
\pce{} maps as finite vector spaces \afnote{The section~\ref{sec:math} is devoted to present an analytical diagonalization of the the Choi matrix for
arbitrary \pce{} maps, and to provide a characterization of completely positive maps by interpreting
\pce{} maps as finite vector spaces}. In section~\ref{sec:generators} we study
generators of the semigroup structure of the set of \pce{} channels, and use
them to derive meaningful physical interpretations of \pce{} channels in
section~\ref{sec:kraus}, as well Kraus operators of the generators.
%
\afnote{We study the
generators of the semigroup structure associated to the set of \pce{} channels in section~\ref{sec:generators}, and we use
them to derive meaningful physical interpretations of \pce{} channels in
section~\ref{sec:kraus}, as well Kraus operators of the generators.}
% 
\afnote{No entendí que se quiere decir con ``as well Kraus operators of the generators"} To finish, we conclude in section~\ref{sec:conclusions}.
% }}}

>>>>

\par
In this work we present a generalization of idempotent Pauli channels, \ie{}
the qubit flip operations (bit, phase and bit-phase when the flip probability is $1/2$), total depolarizing qubit
channel and the identity channel, to the case of $N$ qubits. 
% \cpnote{Mencionar decoherencia} 
The generalization is done by extending
Pauli observables to \textit{Pauli strings} (tensor products of Pauli
matrices)~\cite{KIMURA2003339,Lawrence2002}, the resulting maps are unital and
diagonal in the Pauli strings' basis.
In addition, these channels describe the decoherence process in a similar way
as the aforementioned
ones for the single-qubit case.
From now on we refer to these maps as \textit{Pauli component erasing} (\pce{})
maps. We
derive necessary and sufficient conditions for such mappings to be completely
positive trace preserving, thus, showing which idempotent operations are valid
quantum channels (\pce{} channels). Additionally, we characterize the algebraic
properties of the set of \pce{} channels, showing that it is equipped
with a semigroup structure, which is later used to derive physical
implementations.
%
\par
The paper is organized as follows, in section~\ref{sec:pce_maps} we recall
the properties of quantum channels needed to proceed with the definition 
of 
% the tools to unders
% refreshing of quantum channels theory and the definition of 
\pce{} maps. In
section~\ref{sec:math} we diagonalize analytically the Choi matrix for
arbitrary \pce{} maps and characterize completely positive maps by interpreting
\pce{} maps as finite vector spaces. 
We study the
generators of the semigroup structure associated to the set of \pce{} channels in section~\ref{sec:generators}, and we use
them to derive meaningful physical interpretations of \pce{} channels in
section~\ref{sec:kraus}, as well Kraus operators of the generators.
% 
To finish, we conclude in section~\ref{sec:conclusions}.
% }}}
